Andres Karjus

### 2019-04-09 index.Rmd
news

@@

- "Modelling lexical interactions in diachronic corpora": poster presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an [online version with interactive plots](https://andreskarjus.github.io/isle_poster) and an extended appendix.

>>>>

- Edinburgh Language Lunch 11.04: will be re-presenting the "Modelling lexical interactions in diachronic corpora" poster, originally presented at the [Inaugural ISLE workshop](https://www.comparativelinguistics.uzh.ch/en/events/ISLE-inaugural-workshop.html), here is an [online version with interactive plots](https://andreskarjus.github.io/isle_poster) and an (updated!) appendix.

@@
